Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-12 paper/synthesis.tex
Fixed Contiguity Types citation

A filter is intended to be very simple; it is expected to have one
input port and one output; messages on the input that the filter
policy admits pass unchanged to the output port; all others are not
passed on. We have explored in our work two kinds of filter. In the
first, a relatively shallow scan of the input buffer can enforce the
policy. For example, we have used the expressive power of contiguity
types \cite{contig} to enforce \emph{lightweight} bounds constraints
on GPS coordinates in UxAS messages. On the other hand, the second
kind of filter will parse the input buffer into a data structure
specified in AGREE and apply an user-defined \emph{well-formedness}
property, also specified in AGREE, to the data. This allows
arbitrarily complex well-formedness checking.

>>>>

A filter is intended to be very simple; it is expected to have one
input port and one output; messages on the input that the filter
policy admits pass unchanged to the output port; all others are not
passed on. We have explored in our work two kinds of filter. In the
first, a relatively shallow scan of the input buffer can enforce the
policy. For example, we have used the expressive power of Contiguity
Types \cite{contiguity-types} to enforce \emph{lightweight} bounds constraints
on GPS coordinates in UxAS messages. On the other hand, the second
kind of filter will parse the input buffer into a data structure
specified in AGREE and apply an user-defined \emph{well-formedness}
property, also specified in AGREE, to the data. This allows
arbitrarily complex well-formedness checking.
